Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-21 ms.tex
fixing up captions and other minor edits

\begin{figure}
\begin{center}
\epsfig{file=zp_857.eps, width=3.4in}
\caption{\label{fig:fdsref} Scatterplot of $\mathcal{F}_{857}$ versus 
$\mathcal{I}_{857}$, illustrating our absolute zero point determination by
comparison to the FDS99 prediction for \PLANCK~857 GHz.}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\epsfig{file=dipole_all_100.eps, width=3.4in}
\caption{\label{fig:dip}  Scatter plots of \PLANCK~100, 143, 217, 353, and 545 
GHz versus \PLANCK~857 GHz. Left: before applying zero-level offsets and 
additional low-order corrections. Right: after correcting for the best-fit 
offset and residual Solar dipole (143-545 GHz). 100 GHz is shown after applying
the spherical harmonic correction of Equation \ref{equ:harm}. The dashed red 
line shows the best-fit linear relationship in all cases.}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
\epsfig{file=harm_100.eps, width=6.5in}
\caption{\label{fig:harm} Summary of low-order corrections at 100 GHz. Left: 
prior to our low-order corrections, a $\sim$17$\mu$K zero-level offset is 
present and strong low-order problems reduce the linearity of the 100 GHz 
scatter versus 857 GHz. Center: scatter plot versus 857 GHz after applying the 
best-fit offset and residual Solar dipole corrections derived with Equation 
\ref{equ:dip} to \PLANCK~100 GHz. The correlation is strengthened, but remains
far less tight than for 143-545 GHz (see Figure \ref{fig:dip}, top four rows, 
right column). Right: after applying the spherical harmonic correction of
Equation \ref{equ:harm} to \PLANCK~100 GHz, the correlation versus 857 GHz is 
far more tightly linear than following the dipole correction.}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\epsfig{file=dirbe_slopes.eps, width=6.5in}
\caption{\label{fig:dirbe_slopes} Linear fits of DIRBE 240$\mu$m (left), 
140$\mu$m (center), and 100$\mu$m (right) as a function of \PLANCK~857 GHz. The
red lines illustrate the DIRBE correlation slopes used in our global parameter 
analysis of $\S$\ref{sec:global}.}
\end{center}
\end{figure*}

@@

In the case of the two-component model, based on a spectrum of \PLANCK~and 
DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
$\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall spectrum 
normalization $n$. The constraints we employ are the correlation slopes of each
of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
(2141 GHz) and 240$\mu$m (1250 GHz) relative to \PLANCK~857 GHz, i.e. 
$dI_{\nu_i}/dI_{857}$. We will refer to the slope for band $\nu_i$ relative to 
\PLANCK~857 GHz as $s_{i,857}$. The slopes for \PLANCK~100-545 GHz are taken 
to be those derived from the relative zero level fits of $\S$\ref{sec:relzero},
and are illustrated by the dashed red lines in the right-hand column plots of 
Figure \ref{fig:dip}. The 857 GHz slope is unity by definition.

At 1250, 2141 and 3000 GHz, we use the SFD98-reprocessed DIRBE maps. For each
DIRBE band, we determine $s_{i, 857}$ by performing a linear fit to DIRBE as a 
function of \PLANCK~857 GHz, after both have been zodiacal light subtracted and
smoothed to $1^{\circ}$ FWHM, also restricting to the low HI mask of 
$\S$\ref{sec:relzero} (see Figure \ref{fig:dirbe_slopes}).
% re-mention nside=64 or just bag it?
% restricted to same low HI mask as in Sect. 3.5.2 analysis
% sentence pointing to figure showing the regressions

@@

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Light green
crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
based on our MCMC sampling of the posterior. The posterior distributions are in
general extremely well-behaved, showing no multimodality or other pathological 
qualities. Our MCMC parameter and uncertainty estimates are in good agreement 
with the gridded posteriors. The colorscale is linear in $log(P)$, with black 
representing the maximum of $log(P)$ and white representing $max(log(P))-5$. 
Left: Low S/N pixel at high latitude in the Galactic north. Center: High S/N 
pixel in the Polaris region. Right: Low S/N pixel at high latitude in the 
Galactic south.}
\end{center}
\end{figure*}

@@

However, we found that changing the zero level offsets of the input maps 
had a significant effect on the strength of the anticorrelation between median 
reddening residual and $T_2$. In particular, we experimented with perturbing 
the zero level offset of \PLANCK~857 GHz while correspondingly changing the 
zero levels of the remaining \PLANCK~maps based on the prescription of 
$\S$\ref{sec:relzero}. We also experimented with changing the zero level of SFD
\verb|i100|, independent of the other zero levels. Unfortunately, completely
flattening the reddening residual dependence on $T_2$ required unreasonably 
large zero level modifications. For example, flattening the $T_2$ residual 
required adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Such an offset is 
implausible, being an order of magnitude larger than the nominal \verb|i100| 
zero level uncertainty quoted by SFD98, and comparable to the entire 3000 GHz 
CIB monopole signal. Furthermore, we note that even these large zero 
level modifications had virtually no effect in eliminating the reddening 
residual `bend' versus $E(B-V)_{SFD}$. Thus, changing the zero level 
offsets showed hints of promise in rectifying the reddening residual 
temperature dependence, but cannot completely resolve the systematic trends in 
reddening residuals.
% last few words here are kind of bad, need better terminology

>>>>

\begin{figure}
\begin{center}
\epsfig{file=zp_857.eps, width=3.4in}
\caption{\label{fig:fdsref} Scatter plot of FDS99-predicted 857 GHz thermal
dust emission versus \PLANCK~857 GHz observations, illustrating our absolute 
zero level determination described in $\S$\ref{sec:zp_abs}.}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\epsfig{file=dipole_all_100.eps, width=3.4in}
\caption{\label{fig:dip}  Scatter plots of \PLANCK~100, 143, 217, 353, and 545 
GHz versus \PLANCK~857 GHz. Left: before applying our best-fit zero level 
offsets and additional low-order corrections. Right, top four panels: 
\PLANCK~143-545 GHz after correcting for the best-fit offset and residual Solar
dipole. Bottom right: \PLANCK~100 GHz after applying the spherical harmonic 
corrections of Equation \ref{equ:harm}. The dashed red line shows the best-fit 
linear relationship in all cases.}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
\epsfig{file=harm_100.eps, width=6.5in}
\caption{\label{fig:harm} Summary of low-order corrections at 100 GHz. Left: 
prior to our low-order corrections, a $\sim$17$\mu$K zero level offset is 
present and strong low-order problems reduce the linearity of the 100 GHz 
trend versus 857 GHz. Center: scatter plot of \PLANCK~100 GHz versus 857 GHz 
after applying the best-fit offset and residual Solar dipole corrections 
derived with Equation \ref{equ:dip} to \PLANCK~100 GHz. The correlation is 
strengthened, but remains far less tight than for 143-545 GHz (see right 
column of Figure \ref{fig:dip}, top four rows). Right: after applying the 
spherical harmonic corrections of Equation \ref{equ:harm} to \PLANCK~100 GHz, 
the correlation versus 857 GHz is far more tightly linear than following the 
dipole correction.}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\epsfig{file=dirbe_slopes.eps, width=6.5in}
\caption{\label{fig:dirbe_slopes} Linear fits of SFD-reprocessed DIRBE 
240$\mu$m (left), 140$\mu$m (center), and 100$\mu$m (right) as a function of 
\PLANCK~857 GHz. The red lines illustrate the DIRBE correlation slopes used in 
our dust emission model optimization of $\S$\ref{sec:global}.}
\end{center}
\end{figure*}

@@

In the two-component model case, based on a spectrum of \PLANCK~and 
DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
$\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall spectrum 
normalization $n$. The constraints we employ are the correlation slopes of each
of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
(2141 GHz) and 240$\mu$m (1250 GHz) relative to \PLANCK~857 GHz, i.e. 
$dI_{\nu_i}/dI_{857}$. We will refer to the slope for band $\nu_i$ relative to 
\PLANCK~857 GHz as $s_{i,857}$. The slopes for \PLANCK~100-545 GHz are taken 
to be those derived from the relative zero level fits of $\S$\ref{sec:relzero},
and are illustrated by the dashed red lines in the right-hand column plots of 
Figure \ref{fig:dip}. The 857 GHz slope is unity by definition.

At 1250, 2141 and 3000 GHz, we use the SFD-reprocessed DIRBE maps. For each
DIRBE band, we determine $s_{i, 857}$ by performing a linear fit to DIRBE as a 
function of \PLANCK~857 GHz, after both have been zodiacal light subtracted and
smoothed to $1^{\circ}$ FWHM, also restricting to the low HI mask of 
$\S$\ref{sec:relzero} (see Figure \ref{fig:dirbe_slopes}).
% re-mention nside=64 or just bag it?
% restricted to same low HI mask as in Sect. 3.5.2 analysis
% sentence pointing to figure showing the regressions

@@

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Light green
crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
based on our MCMC sampling of the posteriors. The posterior distributions are 
in general extremely well-behaved, showing no multimodality or other 
pathological qualities. Our MCMC parameter and uncertainty estimates are in 
good agreement with the gridded posteriors. The colorscale is linear in 
$log(P)$, with black representing the maximum of $log(P)$ and white 
representing $max(log(P))-5$. Left: Low S/N pixel at high latitude in the 
Galactic north. Center: High S/N pixel in the Polaris region. Right: Low S/N 
pixel at high latitude in the Galactic south.}
\end{center}
\end{figure*}

@@

However, we found that changing the zero level offsets of the input maps 
had a significant effect on the strength of the anticorrelation between median 
reddening residual and $T_2$. In particular, we experimented with perturbing 
the zero level offset of \PLANCK~857 GHz while correspondingly changing the 
zero levels of the remaining \PLANCK~maps based on the prescription of 
$\S$\ref{sec:relzero}. We also experimented with changing the zero level of SFD
\verb|i100|, independent of the other zero levels. Unfortunately, completely
flattening the reddening residual dependence on $T_2$ required unreasonably 
large zero level modifications. For example, flattening the $T_2$ residual 
required adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Such an offset is 
implausible, being an order of magnitude larger than the nominal \verb|i100| 
zero level uncertainty quoted by SFD, and comparable to the entire 3000 GHz CIB
monopole signal. Furthermore, we note that even these large zero level 
modifications had virtually no effect in eliminating the reddening residual 
`bend' versus $E(B-V)_{SFD}$. Thus, changing the zero level offsets showed 
hints of promise in rectifying the reddening residual temperature dependence, 
but cannot completely resolve the systematic trends in reddening residuals.
% last few words here are kind of bad, need better terminology
